Trends of SDR in Thessaloniki

### 2023-07-04 Article.Rmd
Commit 2023-07-04 11:12

suppressMessages(
    gather_citations(
        sourcefile   = "./Article.Rmd",
        mainreposit  = "./Mainreferences.bib",
        localreposit = "./references.bib",
        folderlink   = "./References_links",
        workingdir   = "~/MANUSCRIPTS/2022_sdr_trends/"
    )
)
```

>>>>

suppressMessages(
    gather_citations(
        sourcefile   = "~/MANUSCRIPTS/2022_sdr_trends/Article.Rmd",
        mainreposit  = "~/MANUSCRIPTS/2022_sdr_trends/Mainreferences.bib",
        localreposit = "~/MANUSCRIPTS/2022_sdr_trends/references.bib",
        folderlink   = "~/MANUSCRIPTS/2022_sdr_trends/References_links",
        workingdir   = "~/MANUSCRIPTS/2022_sdr_trends/"
    )
)
```
